Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals

### 2021-10-13 09_Article/01_Revision1_Reviewers/Simon_2021_Bone_Manuscript_Revised.tex
Added comment on TMD and BV/TV influences on mechanics

	In conclusion, OI trabecular bone from the distal tibia analysed in the present study had similar morphology compared to those reported in the literature. \Add{In particular, we confirmed a significantly lower volume fraction of OI trabecular bone compared to healthy controls that points towards a lower bone strength independently of potentially compromised bone matrix material properties. We also observed a higher tBMD}
	We could not find statistically significant differences in fabric-elasticity relationships between healthy and OI trabecular bone, when the ROIs were homogeneous enough \Add{to trust the computational homogenisation methodology} (i.e. CV lower than 0.263), and were matched for BV/TV and DA. \Add{Therefore, HR-pQCT-based hFE analyses used for bone stiffness estimation of healthy individuals can be used for OI diagnosed patients as well.} \Del{Indermaur et al.\cite{Indermaur2021} found that the compressive behaviour of OI bone extra\-cellular matrix is not inferior to healthy control at the ECM level. Similar results for tensile properties at the extracellular matrix level would indicate that fabric-strength relationships may be similar as well. Under this hypothesis, fragility of OI bone should mainly be explained by thin cortices and low BV/TV of the trabecular compartment.}

>>>>

	In conclusion, OI trabecular bone from the distal tibia analysed in the present study had similar morphology compared to those reported in the literature. \Add{In particular, we confirmed a significantly lower volume fraction of OI trabecular bone compared to healthy controls that points towards a lower bone strength independently of potentially compromised bone matrix material properties. We also observed a 4\% higher TMD in OI which suggest, according to the results of \citeauthor{Indermaur2021}\cite{Indermaur2021}, an increase in ultimate stress about 2\%. %Figure7A y = 0.59x%
	However, this light increase is largely overcome by the lower BV/TV observed (\textasciitilde 26\% less) in OI. According to the results of \citeauthor{Panyasantisuk2015}\cite{Panyasantisuk2015}, this lower volume fraction leads to a decrease about 45\% in stiffness.} %(74**2-100**2)/100**2
	We could not find statistically significant differences in fabric-elasticity relationships between healthy and OI trabecular bone, when the ROIs were homogeneous enough \Add{to trust the computational homogenisation methodology} (i.e. CV lower than 0.263), and were matched for BV/TV and DA. \Add{Therefore, HR-pQCT-based hFE analyses used for bone stiffness estimation of healthy individuals can be used for OI diagnosed patients as well.} \Del{Indermaur et al.\cite{Indermaur2021} found that the compressive behaviour of OI bone extra\-cellular matrix is not inferior to healthy control at the ECM level. Similar results for tensile properties at the extracellular matrix level would indicate that fabric-strength relationships may be similar as well. Under this hypothesis, fragility of OI bone should mainly be explained by thin cortices and low BV/TV of the trabecular compartment.}
